Supplementary material

### 2021-09-03 submission/supplement.rmd
add table with models selected with the adaptive approach

 knitr::kable(
    metrics,
    format      = "latex",
    align       = "l",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    col.names = c(
      "Model",
      "C",
      "ICI",
      "AIC"
    ),
    caption    = "Performance metrics of the different methods used to predict benefit of tPA on 30-day mortality using data from the GUSTO-I trial."
  ) 
```

>>>>

 knitr::kable(
    metrics,
    format      = "latex",
    align       = "l",
    booktabs    = TRUE,
    digits      = 4,
    format.args = list(
      big.mar      = ",",
      decimal.mark = "."
    ),
    col.names = c(
      "Model",
      "C",
      "ICI",
      "AIC"
    ),
    caption    = "Performance metrics of the different methods used to predict benefit of tPA on 30-day mortality using data from the GUSTO-I trial."
  ) %>%
   kable_styling(latex_options = "HOLD_position")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(kableExtra)
library(flextable)

analysisIds <- read_csv(
  here("data/processed/analysisIds.csv"),
  col_types = "iffiiddddddddddddd"
)

interactionAnalysisIds <- read_csv(
  here::here("data/processed/analysisIdsInteractions.csv")
)

dat1 <- readr::read_csv(here::here("data/processed/adaptiveModel.csv")) %>%
  filter(scenarioId < 64) %>%
  group_by(scenarioId) %>%
  nest() %>% 
  mutate(
    test = lapply(data, plyr::count),
    n = lapply(data, nrow)
  ) %>%
  select(scenarioId, test, n) %>%
  arrange(scenarioId) %>%
  unnest(c(test, n)) %>%
  mutate(
    perc = round(freq / n, 2),
    model = ifelse(
      selectedAdaptiveModel == "RCS with 3 knots",
      "rcs",
      selectedAdaptiveModel
    )
  ) %>%
  ungroup() %>%
  select(scenarioId, model, perc) %>%
  spread(model, perc) %>%
  replace(is.na(.), 0) %>%
  left_join(analysisIds, by = c("scenarioId" = "scenario")) %>%
  select(
    type,
    effectSize,
    sampleSize,
    auc,
    treatment,
    risk,
    rcs
  )

dat2 <- readr::read_csv(here::here("data/processed/adaptiveModel.csv")) %>%
  filter(scenarioId >= 64) %>%
  group_by(scenarioId) %>%
  nest() %>% 
  mutate(
    test = lapply(data, plyr::count),
    n = lapply(data, nrow)
  ) %>%
  select(scenarioId, test, n) %>%
  arrange(scenarioId) %>%
  unnest(c(test, n)) %>%
  mutate(
    perc = round(freq / n, 2),
    model = ifelse(
      selectedAdaptiveModel == "RCS with 3 knots",
      "rcs",
      selectedAdaptiveModel
    )
  ) %>%
  ungroup() %>%
  select(scenarioId, model, perc) %>%
  spread(model, perc) %>%
  replace(is.na(.), 0) %>%
  left_join(interactionAnalysisIds, by = c("scenarioId" = "scenario")) %>%
  select(
    type,
    effectSize,
    sampleSize,
    auc,
    treatment,
    risk,
    rcs
  )

dat <- dat1 %>% bind_rows(dat2)

colourer <- scales::col_quantile(
  palette = c("#e5f5f9", "#2ca25f"),
  domain = c(0, 1),
  n = 20
)

flextable(dat) %>%
  theme_booktabs(bold_header = TRUE) %>%
  bg(
    bg = colourer,
    j = c("treatment", "risk", "rcs"),
    part = "body"
  ) %>%
  set_caption("Rates at which the adaptive approach selected each model type.")
```
